Papers

### 2023-10-25 papers.qmd
add accepted envirometrics paper

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, accepted, 2023. [arxiv preprint](https://arxiv.org/abs/2211.12687)

>>>>

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, 10.1002/env.2826, 2023. [PDF](Papers/Envirometics23_ElasticChangeDetection.pdf)
